Probability of causal contact between interstellar civilizations through MonteCarlo simulations

### 2019-07-30 manuscript.tex
github connection test
tratando de cambiar el estilo de latex

\jname{International Journal of Astrobiology}%

@@

\received{xx xxxx xxxx}
\revised{xx xxxx xxxx}
\accepted{xx xxxx xxxx}

@@

A common approach to discuss the possible number of extraterrestrial
intelligent civilizations (ETI) has been the use of the Drake equation
\citep{Gleiser2010, Prantzos2013, Haqq-Misra2017}.
%
However, the uncertainties in the factors make it less prone to a
formal application to define searching strategies or to compute
actual numbers, but is used to organize the discussion instead.
%
Some modifications to the original idea of the equation have tried to
imprint a stochastic nature, or to propose a probabilistic approach,
or to consider the temporal structure which is missing in the
equation.
%
Temporal aspects of the distribution of communicating civilizations
and their contacts have also been explored by several authors
\citep{Fogg1987, Forgan2011, Balbi2018},
%The Impact of the Temporal Distribution of Communicating Civilizations on Their Detectability
%Temporal dispersion of the emergence of intelligence: an inter-arrival time analysis
%The spatiotemporal aspects of SETI
%
as well as efforts on considering the stochastic nature of the Drake equation
\citep{Glade2011}.
%
The simulation approach has also benn considered
\citep{Forgan2008, Forgan2010}.
%New numerical determination of habitability in the Galaxy: the SETI connection

@@

%%%%%%%%%%%% Biography text %%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Author Biography}

\aubio{ML.jpeg}{\textbf{Marcelo Lares} received a degree in physics from the University
of A in 1998 and received his Ph.D. degree in communication engineering in
2002. He now holds a research chair at the B institute. His main research
interests are design and optimization of high power microwave power
amplifiers.}

\aubio{JF.jpeg}{\textbf{Jos\'e Funes} received her Diploma in 1997 from the University of
C and received her Ph.D. at the D University in 2001. She became a full
university professor in 2009. She is currently serving as chair of the E
project and is active in the study of Si power electronics.}

>>>>

\jname{Astrobiology}%

@@

@@

A common approach to discuss the possible number of extraterrestrial
intelligent civilizations (ETI) has been the use of the Drake equation
\citep{Gleiser2010, Prantzos2013, Haqq-Misra2017}.
%
However, the uncertainties in the factors make it less prone to a
formal application to define searching strategies or to compute
actual numbers, but is used to organize the discussion instead.
%
Some modifications to the original idea of the equation have tried to
imprint a stochastic nature, or to propose a probabilistic approach,
or to consider the temporal structure which is missing in the
equation.

%
Temporal aspects of the distribution of communicating civilizations
and their contacts have also been explored by several authors
\citep{Fogg1987, Forgan2011, Balbi2018},
%The Impact of the Temporal Distribution of Communicating Civilizations on Their Detectability
%Temporal dispersion of the emergence of intelligence: an inter-arrival time analysis
%The spatiotemporal aspects of SETI
%
as well as efforts on considering the stochastic nature of the Drake equation
\citep{Glade2011}.
%
The simulation approach has also benn considered
\citep{Forgan2008, Forgan2010}.
%New numerical determination of habitability in the Galaxy: the SETI connection

@@
